```{r}
library(sf)
library(spatstat.geom)   
library(spatstat.explore)
library(ggplot2)
library(raster)
library(viridis)
library(units)
library(readr)
library(sf)
library(ggplot2)

```

# Read
## Nairobi boundary
```{r}
# Read shapefile
boundary <- st_read("/Users/wenlanzhang/Downloads/PhD_UCL/Data/Shp/NariobiShp/Shp_from_Constituency/Nairobi_shp_C.shp")
# plot(st_geometry(boundary), col = "lightgrey", main = "Boundary Only")

ggplot(boundary) +
  geom_sf(fill = "lightgrey", color = "black") +
  theme_minimal() +
  labs(title = "Boundary Only")
```


## SVI
```{r}
df <- read.csv("/Users/wenlanzhang/Downloads/PhD_UCL/Data/Waste/img/Correct_SVI.csv")
df <- df[df$img_dir != "ZWL/" & df$img_dir != "Faith/", ]
df <- df[!is.na(df$lon) & !is.na(df$lat) & 
         df$lon != 0 & df$lat != 0, ]
df <- df[!duplicated(df[, c("lon", "lat", "img_dir", "panoid")]), ]
# names(df)
df
```



```{r}
# Reproject points to match the shapefile CRS
points <- st_as_sf(df, coords = c("lon", "lat"), crs = 4326)  # WGS84
points <- st_transform(points, st_crs(boundary))

# points
```



```{r}
points_within <- points[st_within(points, boundary, sparse = FALSE), ]

ggplot() +
  geom_sf(data = boundary, fill = "lightgrey") +
  geom_sf(data = points_within, color = "red", size = 1) +
  theme_minimal() +
  labs(title = "Points on Boundary")

```



# PPP
## Convert points  (sf) to a spatstat window & point pattern (ppp)
```{r}
# ensure metric CRS
points_utm <- st_transform(points_within, 32737) 
boundary_utm  <- st_transform(boundary, 32737)
```



```{r}
# convert window
w <- as.owin(boundary_utm)    # study window for spatstat

# get coords for ppp
coords <- st_coordinates(points_utm)
pp <- ppp(x = coords[,1], y = coords[,2], window = w)
```


## Kernel Density Estimate (KDE) — intuitive hotspot map
```{r}
# choose bandwidth (sigma). Try cross-validation or rule-of-thumb; also test multiple values.
sigma <- 100 # metres (try 25,50,100 etc)

dens <- density(pp, sigma = sigma, edge = TRUE, at = "pixels", eps = c(50,50)) 
# dens is a pixel image (im object)

# convert to raster for ggplot
r <- raster::raster(dens)
# convert raster -> dataframe for ggplot
kde_df <- as.data.frame(r, xy = TRUE)
colnames(kde_df) <- c("x","y","intensity")

ggplot() +
  geom_raster(data = kde_df, aes(x=x, y=y, fill = intensity)) +
  scale_fill_viridis_c() +
  geom_sf(data = boundary_utm, fill = NA, color = "black") +
  # geom_sf(data = points_within, color = "red", size = 0.5) +
  coord_sf() +
  labs(title = "KDE of waste detections (sigma = 50 m)")
```


## Nearest-Neighbour Index (NNI) — global clustering test (simple)

Formula and approach:
- Observed mean nearest-neighbour distance: d_obs = mean(nndist(pp))
- Under CSR, expected mean = `1/(2*sqrt(lambda))` where lambda = n / area
- NNI = d_obs / d_expected. NNI < 1 → clustering.

Monte-Carlo p-value: simulate CSR (same n, inside same window) many times and compare.
```{r}
n <- pp$n
area_m2 <- area.owin(w)        # area in sq. metres
lambda <- n / area_m2

d_obs <- mean(nndist(pp))

d_expected <- 1 / (2 * sqrt(lambda))
NNI <- d_obs / d_expected

# Monte-Carlo: simulate CSR 999 times and compute mean nndist for each
nsim <- 99
sim_means <- numeric(nsim)
set.seed(42)
for(i in seq_len(nsim)){
  simpp <- runifpoint(n, win = w)    # CSR with n events
  sim_means[i] <- mean(nndist(simpp))
}
p_value <- (sum(sim_means <= d_obs) + 1) / (nsim + 1) # one-sided for clustering

list(NNI = NNI, d_obs = d_obs, d_expected = d_expected, p_value = p_value)
```

## Ripley’s K-function (with CSR envelopes)
```{r}
# Ripley's K-function
K <- Kest(pp, correction = "Ripley")
plot(K, main = "Ripley's K-function")
```


```{r}
# Monte Carlo envelope for K
set.seed(42)
K_env <- envelope(pp, Kest, 
                  correction = "border",  # correction = "Ripley", 
                  # nsim = 39,
                  # global = FALSE, savefuns = FALSE,
                  rmax = 5000,
                  # nr = 600
                  )

# Plot
plot(K_env, main = "Ripley's K with CSR Envelope")
```


## Besag’s L-function (variance-stabilized K)
```{r}
# Besag's L-function
L <- Lest(pp, correction = "border")
plot(L, main = "Besag's L-function")
```


```{r}
# Monte Carlo envelope for L
set.seed(42)

L_env <- envelope(
  pp, Lest, nsim = 99,
  correction = "border"
)
plot(L_env, main = "Besag's L with CSR envelope")
# note: L(d) - d interpretation: positive => clustering; negative => inhibition
```

## Pair Correlation Function (pcf)
```{r}
# pcf is noisier; consider smoothing parameters or averaging
pcf_est <- pcf(pp, correction = "Ripley")
plot(pcf_est, main = "Pair Correlation Function (pcf)") 

```


```{r}
# Envelope for pcf (use fewer sims because it's expensive)
pcf_env <- envelope(
  pp, pcf, nsim = 39,
  correction = "Ripley", global = FALSE, savefuns = FALSE,
)
plot(pcf_env, main = "pcf with CSR envelope")
# pcf > 1 indicates clustering at that distance
```

## Inhomogeneous K (if intensity is not constant)

```{r}
# Rule-of-thumb or profile-likelihood bandwidth
sigma1 <- bw.diggle(pp)   # fast
sigma2 <- bw.ppl(pp)      # slower but more robust
sigma1; sigma2
```


```{r}
# estimate intensity with density
lambdahat <- density(pp, sigma = 200, edge = TRUE)
length(lambdahat)

# class(lambdahat) 
# [1] "im"
```


```{r}
# Plot the estimated intensity map (lambdahat)
plot(lambdahat, main = "Estimated Intensity Map (lambdahat)")
# points(pp, pch = 16, cex = 0.5, col = "red")
```


```{r}
# Kinhom (uses lambdahat at point locations)
K_inhom <- Kinhom(pp, lambda = lambdahat, correction = "border")
plot(K_inhom, main = "Inhomogeneous K")
```
这里没定义0假设



```{r}
## 1. Recalculate lambdahat 
# lambdahat <- density(pp, sigma = sigma2, edge = TRUE) 

## 2. Force all negative values to zero
# Use the pmax function (parallel maximum) to take the max of each pixel value and zero.
lambdahat_positive <- eval.im(pmax(0, lambdahat))

plot(lambdahat_positive, main = "Estimated Intensity Map (lambdahat_positive)")

```


```{r}

## 3. Re-run the Envelope Calculation with the corrected intensity
Kinhom_env <- envelope(
  pp, 
  fun = Kinhom,
  nsim = 39,
  correction = "border", 
  global = FALSE, 
  savefuns = FALSE,
  simulate = expression(
    # Use the corrected, positive intensity map here:
    rpoispp(lambda = lambdahat_positive) 
  )
)

plot(Kinhom_env, main = "Inhomogeneous K Envelope (Fixed)")
```
通过 simulate = expression(...) 参数 明确定义了零假设模型。
模型定义： rpoispp(lambda = lambdahat_positive) 定义了 非齐次泊松过程 (IPP)，强度规则由您的 $\hat{\lambda}$ (lambdahat_positive) 给出。结论： 这次检验的是 数据是否比根据 $\hat{\lambda}$ 规则随机放置的点更聚集。
由于您的观测值在包络线内，因此答案是否定的。


```{r}
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```

# Example🧪: Inhomogeneous K-Function
```{r}
# Install and load the necessary library if you haven't already
# install.packages("spatstat.geom")
library(spatstat.geom)

# Use the 'redwood' point pattern, which is known to be clustered
pp <- redwood
```

## Estimate the Intensity ($\hat{\lambda}$)
```{r}
# Estimate the intensity (lambdahat) using kernel smoothing.
# We'll choose a sigma value that is about 1/10th of the window size (80x80)
# Adjusting this value can fix the "zero intensity" issue discussed earlier.
bandwidth <- 8 
lambdahat <- density(pp, sigma = bandwidth)

# Plot the estimated intensity map (lambdahat)
plot(lambdahat, main = "Estimated Intensity Map (lambdahat)")
points(pp, pch = 16, cex = 0.5, col = "red")
```
## 3. Calculate the Inhomogeneous K-function
```{r}
# Calculate the Inhomogeneous K-function
# 'correction = "border"' handles edge effects
K_inhom <- Kinhom(pp, lambda = lambdahat, correction = "border")

# Note: The warning 'fvlabels truncated...' might still appear here,
# but it's safe to ignore or suppress (as shown in the first response).
```


## 4. Plot and Interpret the Result
```{r}
# Plot the result
plot(K_inhom, 
     main = "Inhomogeneous K-function for Redwood",
     legend = TRUE)

# The result for the redwood dataset should show clustering (the solid line 
# should be above the dashed line for small 'r'), indicating that the points 
# are clustered even after accounting for local density variation.
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```

