---
title: "Is clustering explained by population + Waste"
output:
  html_document: default
  pdf_document: default
---

```{r}
library(sf)
library(terra)  
library(spatstat.geom)
library(spatstat.explore)
library(spatstat.model)   
library(spatstat.random)  # rpoispp, rthin
library(ggplot2)
library(viridis)
library(units)
library(readr)
```

# Read
## Nairobi boundary
```{r}
# Read shapefile
boundary <- st_read("/Users/wenlanzhang/Downloads/PhD_UCL/Data/Shp/NariobiShp/Shp_from_Constituency/Nairobi_shp_C.shp")
# plot(st_geometry(boundary), col = "lightgrey", main = "Boundary Only")

ggplot(boundary) +
  geom_sf(fill = "lightgrey", color = "black") +
  theme_minimal() +
  labs(title = "Boundary Only")
```


## SVI
```{r}
df <- read.csv("/Users/wenlanzhang/Downloads/PhD_UCL/Data/Waste/img/Correct_SVI.csv")
df <- df[df$img_dir != "ZWL/" & df$img_dir != "Faith/", ]
df <- df[!is.na(df$lon) & !is.na(df$lat) & 
         df$lon != 0 & df$lat != 0, ]
df <- df[!duplicated(df[, c("lon", "lat", "img_dir", "panoid")]), ]
# names(df)
# df
head(df, 5)

```


```{r}
# Reproject points to match the shapefile CRS
points <- st_as_sf(df, coords = c("lon", "lat"), crs = 4326)  # WGS84
points <- st_transform(points, st_crs(boundary))

# points
```


### Clip to Nairobi
```{r}
points_within <- points[st_within(points, boundary, sparse = FALSE), ]

ggplot() +
  geom_sf(data = boundary, fill = "lightgrey") +
  geom_sf(data = points_within, color = "red", size = 1) +
  theme_minimal() +
  labs(title = "Points on Boundary")

```

## urban poor
```{r}
# Read shapefile
is_shp <- st_read("/Users/wenlanzhang/Downloads/PhD_UCL/Data/Waste/Angela/slumaps_nairobi_sett/slumaps_nairobi_sett.shp")

# Print summary
print(is_shp)

# Plot
plot(is_shp["geometry"])
```

### Clip to Nairobi
```{r}
poor_within <- is_shp[st_within(is_shp, boundary, sparse = FALSE), ]

ggplot() +
  geom_sf(data = boundary, fill = "lightgrey") +
  geom_sf(data = poor_within, color = "blue", size = 1) +
  theme_minimal() +
  labs(title = "Poor on Boundary")

```


## Metric CRS
```{r}
points_utm <- st_transform(points_within, 32737) 
poor_utm <- st_transform(poor_within, 32737) 
boundary_utm  <- st_transform(boundary, 32737)
boundary_utm_v <- vect(boundary_utm)
```


## WorldPop
```{r}
# Read a .tif raster
# r <- rast("/Users/wenlanzhang/Downloads/PhD_UCL/Data/RS/Pop_density/ConstraintIndividualCountries/ken_ppp_2020_constrained.tif")
r <- rast("//Users/wenlanzhang/Downloads/PhD_UCL/Data/RS/Pop_density/UnconstraintIndividualCountries/ken_ppp_2020.tif")
# r <- rast("/Users/wenlanzhang/Downloads/PhD_UCL/Data/RS/Pop_density/PopDensity/ken_pd_2020_1km.tif")
# r <- rast("/Users/wenlanzhang/Downloads/PhD_UCL/Data/RS/Pop_density/ken_pop_2024_CN_100m_R2025A_v1.tif")

# View basic info
r
plot(r)
```

### Clip to Nairobi
```{r}
# Convert sf → SpatVector
boundary_v <- vect(boundary)

# 1. Crop raster to bounding box
r_crop <- crop(r, boundary_v)

# 2. Mask raster to exact polygon shape
r_mask <- mask(r_crop, boundary_v)

# Plot
# plot(r_mask)
# lines(boundary_v, col = "red")


### Reproject
boundary_utm_v <- vect(boundary_utm)

# Reproject raster
r_mask_utm <- project(r_mask, boundary_utm_v)

# Mask again (optional)
r_mask_utm <- mask(r_mask_utm, boundary_utm_v)

r_mask_utm
plot(r_mask_utm)
lines(boundary_utm_v, col = "red")
```

# Binary inside / outside settlements
```{r}
# convert window
w <- as.owin(boundary_utm)    # study window for spatstat

# # assume informal_utm is sf polygon(s) in the same CRS as boundary_utm
# poor_owin <- as.owin(poor_utm)    # window for settlements
# poor_im   <- as.im(poor_owin, W = w)  # 1 inside, 0 outside (on window w)
# plot(poor_im, main = "Informal settlement indicator")


# library(sf)
# library(spatstat.geom)
# 
# # Example: create polygon around points (buffer of 50 m)
# poor_buffer <- st_buffer(st_union(poor_utm), 50)  # 50 units in UTM
# 
# # convert to spatstat window
# poor_owin <- as.owin(poor_buffer)
# 
# # create pixel image inside/outside
# poor_im <- as.im(poor_owin, W = as.owin(w))  # now 1 inside, 0 outside
# plot(poor_im, main = "Informal settlement indicator")
# 


```


# Distance to nearest informal settlement

```{r}
library(sf)
library(spatstat.geom)

# poor_utm is sf POINTS
coords <- st_coordinates(poor_utm)

# study area window w must be an "owin"
w_owin <- as.owin(w)   # if w is sf polygon
                      
# build the ppp object
poor_ppp <- ppp(
  x = coords[,1],
  y = coords[,2],
  window = w_owin
)


```

```{r}
library(spatstat.geom)
poor_ppp <- unique(ppp(
  x = poor_ppp$x,
  y = poor_ppp$y,
  window = poor_ppp$window
))

# extract coords
xy <- cbind(poor_ppp$x, poor_ppp$y)

# find unique rows
unique_xy <- xy[!duplicated(xy), ]

# rebuild ppp
poor_ppp_unique <- ppp(
  x = unique_xy[,1],
  y = unique_xy[,2],
  window = poor_ppp$window
)

poor_ppp_unique
```
```{r}
poor_dist <- distmap(poor_ppp)
plot(poor_dist, main = "Distance to informal settlements")

```

# Core model: “per capita waste” with population as offset
```{r}
eps <- 1e-6  # to avoid log(0)
cov_list <- list(
  pop      = pop_im,
  informal = poor_im   # or informal_dist, depending on choice
)

# Model with pop as offset, informal as predictor
ppm_pop_only <- ppm(pp ~ offset(log(pop + eps)),
                    covariates = cov_list)

ppm_pop_informal <- ppm(pp ~ informal + offset(log(pop + eps)),
                        covariates = cov_list)

summary(ppm_pop_informal)
anova(ppm_pop_only, ppm_pop_informal, test = "LRT")

```


```{r}
cov_list <- list(
  pop      = pop_im,
  dist_inf = poor_dist
)
ppm_pop_dist <- ppm(pp ~ dist_inf + offset(log(pop + eps)),
                    covariates = cov_list)
summary(ppm_pop_dist)

```


```{r}
lambda_full <- predict(ppm_pop_informal)           # fitted λ(u)
lambda_full <- eval.im(pmax(lambda_full, 1e-12))   # avoid zeros

# Inhomogeneous K using the fitted lambda
rmax  <- 0.30 * diameter.owin(w)
rvals <- seq(0, rmax, length.out = 200)

K_full <- Kinhom(pp, lambda = lambda_full, r = rvals,
                 correction = "translate")
plot(K_full, main = "Kinhom under pop + informal λ")

# Global envelope under fitted model
set.seed(1)
env_full <- envelope(pp,
                     fun = Kinhom,
                     simulate = expression(rpoispp(lambda_full)),
                     nsim = 39, lambda = lambda_full,
                     r = rvals, correction = "translate",
                     global = TRUE, verbose = FALSE)
plot(env_full, main = "Global envelope: Kinhom under pop + informal model")

```





# 下面的不是了

## Convert points (sf) to a spatstat window & point pattern (ppp)
```{r}
# convert window
w <- as.owin(boundary_utm)    # study window for spatstat

# get coords for ppp
coords <- st_coordinates(points_utm)
pp <- ppp(x = coords[,1], y = coords[,2], window = w)
```

```{r}
rmax  <- 0.30 * diameter.owin(w)          # safer ceiling for K/L/g
rvals <- seq(0, rmax, length.out = 200)

# rvals <- seq(0, 3000, length.out = 200)   # adjust max distance to suit your study extent

```


# 1) Method A — Scale the WorldPop raster to be an intensity and test with Kinhom
--- Method A: scale WorldPop -> lambda image, then Kinhom + envelopes ---

This treats WorldPop as a spatial weight for expected intensity and rescales it so the expected total number of points equals the observed number.

Notes on Method A: 
- This method assumes proportionality: expected waste point intensity ∝ population density. That may or may not be substantively correct (waste generation could be non-linear with pop).
- Make sure pop_im has no spurious NAs inside your window; mask or set NA→0 if needed (but consider meaningfully).


```{r}
# --- raster (raster::RasterLayer) -> im ---
raster_to_im_fixed <- function(r){
  if(inherits(r, "SpatRaster")) r <- raster::raster(r)
  if(!inherits(r, "RasterLayer")) stop("Input must be RasterLayer or SpatRaster")
  pts <- raster::rasterToPoints(r)   # x, y, val
  xs <- sort(unique(pts[,1]))
  ys <- sort(unique(pts[,2]))
  # IMPORTANT: rows = length(ys), cols = length(xs)
  zmat <- matrix(NA, nrow = length(ys), ncol = length(xs))
  for(k in seq_len(nrow(pts))){
    col_i <- match(pts[k,1], xs)   # x -> column index
    row_j <- match(pts[k,2], ys)   # y -> row index
    zmat[row_j, col_i] <- pts[k,3] # row (y), col (x)
  }
  # build im: xcol = xs (length ncol), yrow = ys (length nrow)
  spatstat.geom::im(zmat, xcol = xs, yrow = ys)
}

# --- terra (SpatRaster) -> im (no raster package conversion) ---
terra_to_im_fixed <- function(tr){
  if(!inherits(tr, "SpatRaster")) stop("Input must be a terra SpatRaster")
  ncell <- terra::ncell(tr)
  coords <- terra::xyFromCell(tr, seq_len(ncell))
  vals <- terra::values(tr)
  pts <- cbind(coords, vals)
  colnames(pts) <- c("x","y","v")
  pts <- pts[!is.na(pts[,"v"]), , drop = FALSE]
  xs <- sort(unique(pts[,"x"]))
  ys <- sort(unique(pts[,"y"]))
  zmat <- matrix(NA, nrow = length(ys), ncol = length(xs))
  for(k in seq_len(nrow(pts))){
    col_i <- match(pts[k,"x"], xs)
    row_j <- match(pts[k,"y"], ys)
    zmat[row_j, col_i] <- pts[k,"v"]
  }
  spatstat.geom::im(zmat, xcol = xs, yrow = ys)
}
```

### Example
```{r}
# # --- Minimal test with a small raster ---
# r_test <- raster(xmn=0, xmx=4, ymn=0, ymx=3, res=1)  # 4 x 3 grid
# values(r_test) <- 1:ncell(r_test)
# plot(r_test, main="raster test")
# im_test <- raster_to_im_fixed(r_test)
# plot(im_test, main="im (constructed)")
```


```{r}
pop_im <- terra_to_im_fixed(r_mask_utm)

pop_im <- eval.im(ifelse(is.na(pop_im), NA, pop_im))  # keep NA outside
# optional: crop to the rectangle of w to avoid stray margins
pop_im <- pop_im[as.rectangle(w), drop = TRUE]

# 1. Visual check
plot(pop_im, main = "Population image (pop_im, raw)")

# 2. Summary / dimensions
dim(pop_im$v)        # matrix dims: rows = length(y), cols = length(x)
length(pop_im$xcol)  # x coordinates (should equal ncol(pop_im$v))
length(pop_im$yrow)  # y coordinates (should equal nrow(pop_im$v))

# 3. Range
range(pop_im$v, na.rm = TRUE)

# 4. Integral (total population mass over image)
total_pop <- integral(pop_im)
total_pop
pop_im
```





```{r}
# Compute integral (sum over area) of pop_im
pop_total <- integral(pop_im)   # integral over spatial domain (units: population * area unit)

# Create a lambda image scaled so that expected number of points equals observed npoints(pp)
lambda_im <- pop_im * (npoints(pp) / pop_total)
lambda_im  <- eval.im(pmax(lambda_im,  1e-12)) # ？

# Visual check
plot(lambda_im, main = "Scaled lambda image (expected points per unit area)")

```


```{r}
# Compute inhomogeneous K function using the population-derived lambda

K_inhom_pop <- Kinhom(pp, lambda = lambda_im, r = rvals, correction = "translate")
plot(K_inhom_pop, main = "Kinhom (using population-derived lambda)")
```


```{r}
# Envelope test: simulate inhomogeneous Poisson with the same lambda image
set.seed(42)
env_pop <- envelope(pp,
                    fun = Kinhom,
                    simulate = expression(rpoispp(lambda_im)),
                    nsim = 39,
                    lambda = lambda_im,
                    r = rvals,
                    correction = "translate",
                    verbose = FALSE)
plot(env_pop, main = "Kinhom with population-based Poisson envelopes")
```


# 2) Method B — Fit an inhomogeneous point-process (ppm) using population as covariate, then test
 --- Method B: fit ppm(pp ~ pop) and use fitted intensity as lambda ---

This fits a log-linear model for point intensity using population as a covariate, then uses the modelled intensity as `lambda` for Kinhom/envelope. This is more flexible: it estimates the relationship rather than forcing it by simple rescaling.

Notes on Method B:
- ppm gives you an estimated relationship (coefficient for `pop`) and a fitted intensity that may better capture how population explains your points. You can also try `ppm(pp ~ offset(log(pop)))` if you believe population should be an offset rather than a predictor (i.e. proportional baseline rate).
- Diagnostics: check `anova(ppm_model)` or `residuals(ppm_model)` if you want more.

```{r}
# Prepare covariate image for ppm: ensure it's named as a covariate
pop_cov <- pop_im    # the population image (same as above)

# Fit a log-linear point process model with population as covariate
# Note: depending on model complexity / sample size you may want to include other covariates or offset(log(pop))
ppm_model <- ppm(pp ~ pop, covariates = list(pop = pop_cov))
summary(ppm_model)
```

```{r}
# Model-based global envelope:
set.seed(42)
EF <- envelope(ppm_model, fun = Kinhom,
               nsim = 39, r = rvals,
               correction = "translate",
               global = TRUE, verbose = FALSE)
plot(EF, main = "Model-based envelope from ppm(pop)")
```


```{r}
# Predict the fitted intensity (lambda) as an "im" object
lambda_fit <- predict(ppm_model)   # returns an image of fitted intensity (units: points per unit area)
lambda_fit <- eval.im(pmax(lambda_fit, 1e-12))  #？

plot(lambda_fit, main = "Fitted intensity from ppm (pop covariate)")

# Kinhom using the fitted intensity
K_inhom_fit <- Kinhom(pp, lambda = lambda_fit, r = rvals, correction = "translate")
plot(K_inhom_fit, main = "Kinhom (using fitted ppm intensity)")

```


```{r}
set.seed(42)
KT <- envelope(pp, fun = Kinhom,
               simulate = expression(rpoispp(lambda_fit)),
               nsim = 39, lambda = lambda_fit, r = rvals,
               correction = "translate",
               global = TRUE, verbose = FALSE)
plot(KT, main = "Global envelope: Kinhom under ppm(pop)")

# One-line formal tests (across r)
dclf.test(pp, Kinhom,
          simulate = expression(rpoispp(lambda_fit)),
          lambda = lambda_fit, nsim = 39)

mad.test(pp,  Kinhom,
         simulate = expression(rpoispp(lambda_fit)),
         lambda = lambda_fit, nsim = 39)

```



```{r}
# Envelope test simulating inhomogeneous Poisson with the fitted lambda
set.seed(42)
env_fit <- envelope(pp, fun = Kinhom,
                    simulate = expression(rpoispp(lambda_fit)),
                    nsim = 39,
                    lambda = lambda_fit,
                    r = rvals,
                    correction = "translate",
                    verbose = FALSE)
plot(env_fit, main = "Kinhom with ppm-fitted Poisson envelopes")
```

# Inhomogeneous with L-function (Linhom) and pair correlation function (pcfinhom)

```{r}
# Inhomogeneous L-function (Linhom)
L_inhom <- Linhom(pp, lambda = lambda_im, r = rvals, correction = "translate")
plot(L_inhom, main = "Linhom (population lambda)")
```

```{r}
L_fit  <- Linhom(pp, lambda = lambda_fit,  r = rvals, correction = "translate")
plot(L_fit, main = "L_fit (population lambda)")

```

```{r}
# Inhomogeneous pair correlation function (pcfinhom)
g_inhom <- pcfinhom(pp, lambda = lambda_im, r = seq(0,3000,by=50))
plot(g_inhom, main = "Inhomogeneous pair correlation (population lambda)")

```

```{r}
g_fit  <- pcfinhom(pp, lambda = lambda_fit, r = seq(0,3000,by=50))
plot(g_fit, main = "Inhomogeneous pair correlation g_fit (population lambda)")
```


```{r}
# Compare L- and g-functions under the two λ’s
L_im   <- Linhom(pp, lambda = lambda_im,  r = rvals, correction = "translate")
L_fit  <- Linhom(pp, lambda = lambda_fit, r = rvals, correction = "translate")

g_im   <- pcfinhom(pp, lambda = lambda_im,  r = seq(0,3000,by=50))
g_fit  <- pcfinhom(pp, lambda = lambda_fit, r = seq(0,3000,by=50))

par(mfrow=c(1,2))
plot(L_im,  main="Linhom (scaled WorldPop λ)",  legend=FALSE)
plot(L_fit, main="Linhom (ppm-fitted λ)",      legend=FALSE)

par(mfrow=c(1,2))
plot(g_im,  main="pcfinhom (scaled WorldPop λ)", legend=FALSE)
plot(g_fit, main="pcfinhom (ppm-fitted λ)",      legend=FALSE)
par(mfrow=c(1,1))

```



```{r}
# Numeric checks
n_bad <- sum(is.na(lambda_im[pp]))
cat("Points falling on NA λ (scaled WorldPop):", n_bad, "\n")
cat("Min/Median/Max λ at points (scaled):",
    min(lambda_im[pp], na.rm=TRUE), median(lambda_im[pp], na.rm=TRUE),
    max(lambda_im[pp], na.rm=TRUE), "\n")

n_bad_fit <- sum(is.na(lambda_fit[pp]))
cat("Points on NA λ (fitted):", n_bad_fit, "\n")

# Histogram of λ values at data points vs. everywhere
lam_pts  <- lambda_im[pp]
lam_field <- as.vector(lambda_im$v)
hist(lam_pts,  breaks=30, main="λ at waste points (scaled WorldPop)", xlab="λ")
hist(lam_field, breaks=30, main="λ across window (scaled WorldPop)",  xlab="λ")

```



```{r}
# Does population improve fit?
m0 <- ppm(pp ~ 1)                    # intercept-only (homogeneous)
m1 <- ppm(pp ~ pop, covariates = list(pop = pop_im))
anova(m0, m1, test="LRT")            # should be highly significant

# Trend vs population (nonparametric) — checks functional form
R <- rhohat(pp, covariate = pop_im)  # intensity vs population
plot(R, main="rhohat: intensity vs population")

# Residual diagnostics
# diagnose(m1, type="qq")              # QQ plot for pixel residuals
# lurking(m1, pop_im)                  # residuals vs population covariate
# spatstat.model::diagnose.ppm(m1, type = "qq")

spatstat.model::diagnose.ppm(m1, type = "raw")            # residual map
spatstat.model::lurking(m1, covariate = pop_im)           # residuals vs pop
```


```{r}
# Points must lie in window and on non-NA lambda
stopifnot(all(inside.owin(pp$x, pp$y, w)))
any_bad <- any(is.na(lambda_im[pp]))
if (any_bad) stop("Some points fall where lambda_im is NA. Fix with flooring/masking.")

# Visual: overlay points on λ
plot(lambda_im, main = "lambda_im + points")
# points(pp, pch = 20, cex = 0.5)
```




## Optional alternative: proportional (offset) model
```{r}
eps <- 1e-6
ppm_off <- ppm(pp ~ offset(log(pop + eps)), covariates = list(pop = pop_im))
envelope(ppm_off, Kinhom, nsim=39, r=rvals, correction="translate")
```



```{r}
eps <- 1e-6
ppm_off <- ppm(pp ~ offset(log(pop + eps)),
               covariates = list(pop = pop_im))

set.seed(1)
EF_off <- envelope(ppm_off, fun = Kinhom,
                   nsim = 39, r = rvals,
                   correction = "translate",
                   global = TRUE, verbose = FALSE)
plot(EF_off, main = "Model-based envelope: offset log(pop)")

```


# Diagnostics section (put after your existing anova, rhohat, and residuals)
```{r}
# (If not already run above)
dclf.test(pp, Kinhom,
          simulate = expression(rpoispp(lambda_fit)),
          lambda = lambda_fit, nsim = 39)
mad.test(pp,  Kinhom,
         simulate = expression(rpoispp(lambda_fit)),
         lambda = lambda_fit, nsim = 39)

```


# Optional “Model validation (super-thinning)” section (end of document)

```{r}
library(spatstat.random)

# Pick a target constant rate (common choice: median of fitted λ)
lam0 <- median(as.vector(lambda_fit$v), na.rm = TRUE)

# Make sure λ̂ has no zeros/NA inside the window
lambda_fit <- eval.im(pmax(lambda_fit, 1e-12))
lambda_fit <- eval.im(ifelse(is.na(lambda_fit), 1e-12, lambda_fit))

# Thinning probability as an IMAGE: P(x) = min(1, lam0 / λ̂(x))
Pimage <- eval.im(pmin(1, lam0 / lambda_fit))

# Thin using the image (no length-mismatch possible)
pp_thin <- rthin(pp, P = Pimage)
 
# Fill deficits so the result is ~ CSR at rate lam0
resid_im <- eval.im(pmax(0, lam0 - lambda_fit))
resid_im <- eval.im(ifelse(is.na(resid_im), 0, resid_im))
pois_sup <- rpoispp(resid_im)

pp_super <- superimpose(pp_thin, pois_sup)

# Test against CSR (use explicit CSR sims at rate lam0 on the same window)
set.seed(1)
env_super <- envelope(
  pp_super, fun = Kest, r = rvals, nsim = 199,
  simulate = expression(rpoispp(lam0, win = Window(pp_super))),
  correction = "translate", global = TRUE, verbose = FALSE
)
plot(env_super, main = "Super-thinned pattern vs CSR (Kest)")

```



| **Method**                                                      | **Population considered?** | **How population enters the model**                                                                         | **Null hypothesis / Expected result if population explains pattern**                      | **Interpretation if observed > expected (above envelope)**                                                  |
| --------------------------------------------------------------- | -------------------------- | ----------------------------------------------------------------------------------------------------------- | ----------------------------------------------------------------------------------------- | ----------------------------------------------------------------------------------------------------------- |
| **1. K<sub>inhom</sub> (simple Poisson, no covariate)**         | ❌ No                       | None – assumes uniform intensity across space                                                               | Waste points follow a homogeneous Poisson process (completely random)                     | Clustering exists overall (hotspots) — pattern not random                                                   |
| **2. K<sub>inhom</sub> (using scaled WorldPop λ)**              | ✅ Yes                      | WorldPop raster is scaled so that expected total points = observed total                                    | Waste points follow an inhomogeneous Poisson process where intensity ∝ population density | Clustering beyond population — other spatial drivers (e.g. infrastructure, socio-environmental factors)     |
| **3. K<sub>inhom</sub> (using fitted PPM intensity)**           | ✅ Yes                      | λ(x, y) estimated by a fitted **ppm** model: `ppm(pp ~ pop)` (log-linear dependence on population)          | Waste distribution matches a population-dependent intensity surface                       | Significant clustering beyond the fitted intensity indicates residual aggregation unexplained by population |
| **4. K<sub>inhom</sub> (using PPM with offset log(pop))**       | ✅ Yes (fixed baseline)     | Population used as an *offset*: `ppm(pp ~ offset(log(pop)))` → assumes strict proportionality to population | Waste expected exactly proportional to population                                         | Clustering above envelope means waste is *more* spatially concentrated than population alone predicts       |
| **5. L<sub>inhom</sub> / Pair correlation (g<sub>inhom</sub>)** | ✅ (if λ supplied)          | Uses same λ image as K<sub>inhom</sub>                                                                      | Same as above — randomness conditional on λ                                               | Values > 1 ( or L(r) > r ) → clustering; < 1 → regularity                                                   |


```{r}
```


```{r}
```


